---
output: pdf_document
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\doublespacing

\section{Appendix A: R Code and Data Preparation for Chapter 3}
\label{sec:Appendix A: R Code and Data Preparation for Chapter 3}

\singlespace

Required: R Packages from CRAN

\small
```{r, eval=FALSE, results="hide", fig.show="hide", fig.keep="none", echo=TRUE}
if (!require(caTools)){
  install.packages("caTools")
  library(caTools)
}
if (!require(caret)){
  install.packages("caret")
  library(caret)
}
if (!require(R2HTML)){
  install.packages("R2HTML")
  library(R2HTML)
}
if (!require(rattle)){
  install.packages("rattle")
  library(rattle)
}
if (!require(magrittr)){
  install.packages("magrittr")
  library(magrittr)
}
if (!require(dplyr)){
  install.packages("dplyr")
  library(dplyr)
}
if (!require(Hmisc)){
  install.packages("Hmisc")
  library(Hmisc)
}
if (!require(chron)){
  install.packages("chron")
  library(chron)
}  
  if (!require(ggplot2)){
  install.packages("ggplot2")
  library(ggplot2)
  }
```
\normalsize

\subsection{Data preparation for understanding the raw frequency and raw severity data mentioned in
section \ref{sec:Exploratory data analysis} on page \pageref{sec:Exploratory data analysis} of collected internally over the period
between 1 January 2013 and 31 March 2013 i.e., Q12013 at an investment bank in SA}
\label{ssec:Data preparation raw}

\small
```{r, eval=FALSE, echo=TRUE}
file_loc <- "C:/Users/Mphekeleli/Documents/R PROJECT/OpRiskPHDGitHub
/OpRisk_PHD_Thesis/Data"
setwd(file_loc)
list.files(file_loc)
frequency <- openxlsx::read.xlsx("Raw_Formatted_Data.xlsx",
                      check.names = TRUE, sheet = "Frequency")
severity <- openxlsx::read.xlsx("Raw_Formatted_Data.xlsx",
                      check.names = TRUE, sheet = "Severity")
projdata <- openxlsx::read.xlsx("OPriskDataSet_exposure.xlsx",
                      check.names = TRUE, sheet = "CleanedData")
```
\normalsize

\subsection{Data preparation providing the numbers of OpRisk events collected through pre-processing by following the LCDE as described in section \ref{sec:Description of the dataset} on \pageref{sec:Description of the dataset} over Q12013, limited to the covariates selected to fit into the models}
\label{ssec:Data preparation pre-processed}

\small
```{r, eval=FALSE, echo=TRUE}
# Set parameter values
crv$seed <- 42 # set random seed
crv$training.proportion <- 1.0

# Load data
fname <- "file:///G:/PHD/OPRISK_PHD_DISS/Data/OPriskDataSet_exposure.csv"
crs$dataset <- read.csv(fname,
              sep=";",
              dec=",",
              na.strings=c(".", "NA", "", "?"),
              strip.white=TRUE, encoding="UTF-8")

# Build the train/validate/test datasets.

# nobs=2330 train=2330 validate=0 test=0
set.seed(crv$seed)
crs$nobs   <- nrow(crs$dataset)
crs$sample <- sample(crs$nobs, crv$training.proportion * crs$nobs)
crs$train  <- crs$sample <- sample(crs$nobs, crv$training.proportion * crs$nobs)
# crs$train  <- sample(crs$nobs, 1*crs$nobs)
crs$validate <- NULL
crs$test <- NULL

# The following variable selections have been noted.
crs$input     <- c("Trade", "UpdatedDay", "UpdatedTime",
                   "TradedDay", "TradedTime", "Desk", "CapturedBy",
                   "TradeStatus", "TraderId", "Instrument", "Reason",
                   "Loss", "EventTypeCategoryLevel1",
                   "BusinessLineLevel1", "exposure")

crs$numeric   <- c("Trade", "UpdatedDay", "UpdatedTime",
                   "TradedDay", "TradedTime", "Loss", "exposure")

crs$categoric <- c("Desk", "CapturedBy", "TradeStatus",
                   "TraderId", "Instrument", "Reason",
                   "EventTypeCategoryLevel1", "BusinessLineLevel1")

crs$target    <- "LossIndicator"
crs$risk      <- NULL
crs$ident     <- NULL
crs$ignore    <- c("UpdateTime", "TradeTime", "Nominal", "FloatRef", 
                   "LastResetDate", "LastResetRate", "Theta", "Unexplained")
crs$weights   <- NULL
```
\normalsize

\subsection{The algorithm only accepts numerical data and so categorical data is transformed into numeric. This is done using an approach where each value of a categoric variable is turned into a variable itself. Multi-level categoric variables are recoded by building dummy variables corresponding to each level by the following commands:}
\label{ssec:Transforming to dummy variables}

Numerical and categoric variables (to be transformed by below conversion code) depicted in table \ref{tab_contents} on page \pageref{tab_contents}:

\small
```{r, eval=FALSE, echo=TRUE}
# Remap factor variables and transform into numeric variables.
crs$dataset[["TNM_Desk"]] <- as.numeric(crs$dataset[["Desk"]])
crs$dataset[["TNM_CapturedBy"]] <- as.numeric(crs$dataset[["CapturedBy"]])
crs$dataset[["TNM_TraderId"]] <- as.numeric(crs$dataset[["TraderId"]])
crs$dataset[["TNM_Instrument"]] <- as.numeric(crs$dataset[["Instrument"]])
crs$dataset[["TNM_Reason"]] <- as.numeric(crs$dataset[["Reason"]])
crs$dataset[["TNM_EventTypeCategoryLevel1"]] <- as.numeric(crs$dataset
                                        [["EventTypeCategoryLevel1"]])
crs$dataset[["TNM_BusinessLineLevel1"]] <- as.numeric(crs$dataset
                                             [["BusinessLineLevel1"]])
```
\normalsize

\subsection{Scatterplots and Histograms plots of loss severities and frequency counts against selected explanatory variables showing basic
summary statistics of intra-day trading activity}
\label{ssec:Scatterplots and Histograms of intra-day trading activity}

Figures \ref{Intra_Day_Trends} and \ref{Hist_Loss_Freq} on page \pageref{Hist_Loss_Freq}:

\small
```{r, eval=FALSE, echo=TRUE}
# Scatterplots for loss severities
plot(projdata$UpdatedTime, log(projdata$Loss+0.000000001), ylim = c(6, 18),
     col = "navy", xlab = "Updated Time", ylab = "Log. Loss")
xyplot(Loss ~ as.factor(TraderId) , data = projdata)

# Histograms for loss severities
hist(projdata$UpdatedDay, col = "#9999CC", main = "All losses", xlab = "Updated Day"
     , ylab = "Frequency")
hist(projdata$TradedDay)
```
\normalsize

\subsection{Characteristics of exposure: Exposure data is used for several of the steps of the process in frequency and severity modelling}
\label{ssec:Characteristics of exposure}

Figure \ref{Exploration_analysis_exposure} on page \pageref{Exploration_analysis_exposure}:

\small
```{r, eval=FALSE, echo=TRUE}
#######Display histogram plots for the selected variables##########
#============================================================
# Display histogram plots for the selected variables. Use ggplot2 to generate
# histogram plot for exposure. Generate the plot.

Exp <- crs %>%
  with(dataset[train,]) %>%
  dplyr::select(exposure) %>%
  ggplot2::ggplot(ggplot2::aes(x=exposure)) +
  ggplot2::geom_density(lty=1, lwd=1) +
  ggplot2::geom_density(ggplot2::aes(fill="", colour=""), alpha=0.55) +
  ggplot2::xlab("Exposure") +
  ggplot2::ggtitle("Pdf(exposure)") +
  ggplot2::labs(y="Density") +
  theme_bw(base_size = 15) +
  theme(legend.position = "none")

# Display the plots.
gridExtra::grid.arrange(Exp)

#============================================================
# Generate just the data for an Ecdf plot of the variable 'exposure'.
ds <- rbind(data.frame(dat=crs$dataset[crs$train,][,"exposure"], grp="All"))

# The 'Hmisc' package provides the 'Ecdf' function.
library(Hmisc, quietly=TRUE)

# Plot the data.
Ecdf(ds[ds$grp=="All",1], col="red", xlab="exposure", lwd=2, 
     ylab=expression(Proportion <= x), subtitles=FALSE)

# Add a title to the plot.
title(main="Cdf(exposure)")
    
#============================================================
# Benford's Law 

# The 'ggplot2' package provides the 'ggplot' function.
library(ggplot2, quietly=TRUE)

# The 'reshape' package provides the 'melt' function.
library(reshape, quietly=TRUE)

# Initialies the parameters.
var    <- "exposure"
digit  <- 1
len    <- 1

# Build the dataset
ds <- merge(benfordDistr(digit, len),
            digitDistr(crs$dataset[crs$train,][var], digit, len, "All"))

# Plot the digital distribution
p <- plotDigitFreq(ds)
p <- p + ggtitle("Digital Analysis") +
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(6, 6, 6, 6)
    ) +
  # custom box around legend
 theme(
    legend.box.background = element_rect(color="red", size=2),
    legend.box.margin = margin(6, 6, 6, 6)
) +
# custom the key
 theme(legend.key = element_rect(fill = "white", colour = "black")) +
# custom the text
 theme(legend.text = element_text(size = 8, colour = "red")) +
# custom the title
 theme(legend.title = element_text(face = "bold"))
print(p)
# #============================================================
```
\normalsize

\subsection{Histograms for frequency characteristics of daily and monthly operations for daily losses and/or pending/near misses}
\label{ssec:Frequency characteristics of operational activity}

Figures \ref{Exploratory_UpdateTime_Frequency3plot} and \ref{Exploratory_UpdateDay_Frequency3plot} on page \pageref{Exploratory_UpdateTime_Frequency3plot}:

\small
```{r, eval=FALSE, echo=TRUE}
################   EXPLORATORY DATA ANALYSIS  ###################
#___________________________________________________________________________________________________
# Update Time
### summary statistics
 summary(projdata$UpdatedTime)

### Histograms - ALL Losses and Near Misses/Pending Losses and Realised losses 
par(mfrow=c(1,3))
hist(projdata$UpdatedTime, col = "blue", main = "All losses", 
     xlab = "Update Time", ylab = "Frequency")
hist(projdata$UpdatedTime[projdata$LossIndicator == 0], col = "red",
     main = "Near Misses", xlab = "Update Time", ylab = "Frequency")
hist(projdata$UpdatedTime[projdata$LossIndicator == 1], col = "green",
     main = "Realised losses", xlab = "Update Time", ylab = "Frequency")
par(mfrow=c(1,1))
#___________________________________________________________________________________________________
# # Update Day
 summary(projdata$UpdatedDay)

### Histograms - ALL Losses and Near Misses/Pending Losses and Realised losses
par(mfrow=c(1,3))
hist(projdata$UpdatedDay, col = "#9999CC", main = "All losses",
     xlab = "Updated Day", ylab = "Frequency")
hist(projdata$UpdatedDay[projdata$LossIndicator == 0], col = "#CC6666",
     main = "Near Misses", xlab = "Updated Day", ylab = "Frequency")
hist(projdata$UpdatedDay[projdata$LossIndicator == 1], col = "#66CC99",
     main = "Realised losses", xlab = "Updated Day", ylab = "Frequency")
par(mfrow=c(1,1))
```
\normalsize

\subsection{Density plots of overlaid trade proportions of realised losses vs pending losses/near misses}
\label{ssec:Density plots}

Figures \ref{Density_Proportions} on page \pageref{Density_Proportions}:

\small
```{r, eval=FALSE, echo=TRUE}
# Density Plot for Updated Day
p01 <- crs %>%
  with(dataset[sample,]) %>%
  dplyr::mutate(LossIndicator=as.factor(LossIndicator)) %>%
  dplyr::select(UpdatedDay, LossIndicator) %>%
  ggplot2::ggplot(ggplot2::aes(x=UpdatedDay)) +
  ggplot2::geom_density(lty=3) +
  ggplot2::geom_density(ggplot2::aes(fill=LossIndicator, colour=LossIndicator)
                        , alpha=0.55) +
  ggplot2::ggtitle("Distr. of Updated DaY") +
  ggplot2::labs(fill="LossIndicator", y="Density") +
  ggplot2::xlab("Day of Month that Trade Was Updated") +
  ggplot2::theme(legend.position=c(.7,.2))

# Density Plot for Traded day
p02 <- crs %>%
  with(dataset[sample,]) %>%
  dplyr::mutate(LossIndicator=as.factor(LossIndicator)) %>%
  dplyr::select(TradedDay, LossIndicator) %>%
  ggplot2::ggplot(ggplot2::aes(x=TradedDay)) +
  ggplot2::geom_density(lty=3) +
  ggplot2::geom_density(ggplot2::aes(fill=LossIndicator, colour=LossIndicator)
                        , alpha=0.55) +
  ggplot2::ggtitle("Distr. of TradedDay") +
  ggplot2::labs(fill="LossIndicator", y="Density") +
  ggplot2::xlab("Day of Month for Trade") +
  ggplot2::theme(legend.position=c(.7,.2))

# Display the plots.
gridExtra::grid.arrange(p01, p02, nrow = 1)
```
\normalsize

Table \ref{tab_Desk_Prop} on \pageref{tab_Desk_Prop}

\small
```{r, eval=FALSE, echo=TRUE}
# addmargins(table(projdata$Desk, projdata$LossIndicator), 2)
```
\normalsize

\subsection{Histograms of overlaid trade proportions of realised losses vs pending loss/near misses}
\label{ssec:Histogram proportions}

Figures \ref{Desk_Proportions} on page \pageref{Desk_Proportions}:

\small
```{r, eval=FALSE, echo=TRUE}
# Plot Desk category distribution
p03 <- crs %>%
  with(dataset[sample,]) %>%
  dplyr::mutate(LossIndicator=as.factor(LossIndicator)) %>%
  dplyr::select(Desk, LossIndicator) %>%
  dplyr::group_by(Desk, LossIndicator) %>%
  dplyr::summarise(n = n()) %>%
  ggplot2::ggplot(ggplot2::aes(x=Desk, y=n, fill=LossIndicator)) +
  ggplot2::geom_bar(stat="identity") +
  ggplot2::ggtitle("Desk category distribution") +
  ggplot2::theme_minimal() +
  ggplot2::theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  ggplot2::ylab("Frequency")

# Create new variable to proportion no. of realised losses
T01 <- crs %>%
  with(dataset[sample,]) %>%
  dplyr::mutate(LossIndicator=as.factor(LossIndicator)) %>%
  dplyr::select(Desk, LossIndicator) %>%
  dplyr::group_by(Desk, LossIndicator) %>%
  dplyr::summarise(n = n())

T02 <- T01 %>%
  group_by(Desk) %>%
  summarise(N=sum(n))

T03 <- inner_join(T01, T02)

# Plot Desk category by proportion
T04 <- T03 %>%
  mutate(Prob=n/N) %>%
  filter(LossIndicator==1) %>%
  select(Desk, Prob) %>%
  arrange(desc(Prob)) %>%
  ggplot2::ggplot(ggplot2::aes(x=Desk, y=Prob, fill=Desk), alpha=0.55) +
  ggplot2::geom_bar(stat="identity", fill="grey", colour="black", show.legend = FALSE)+
  ggplot2::ggtitle("Proportion of losses per Desk") +
  ggplot2::theme_minimal()+
  ggplot2::theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  ggplot2::ylab("Loss Ratio (n/N)")+
  ggplot2::xlab("Desk")

#Display both plots in one row
gridExtra::grid.arrange(p03, T04, nrow = 1)
####============================================================
```
\normalsize

\subsection{Mosaic grid plots for the bidimensional distributions by traded \texttt{Instrument}, \texttt{TraderId} and number}
\label{ssec:Mosaic bidimensional grid plot}

Figures \ref{Mosaic_Instr_Trd_Tec} on page \pageref{Mosaic_Instr_Trd_Tec}:

\small
```{r, eval=FALSE, echo=TRUE}
par(mfrow=c(1,2))
plot(table(projdata$LossIndicator, projdata$Instrument), main="By Instrument",
     col=rainbow(20), las=1)
plot(table(projdata$LossIndicator, projdata$TraderId), main="By Trader", 
     col=rainbow(20), las=1)
plot(table(projdata$LossIndicator, projdata$CapturedBy), main="By Tech Support",
     col=rainbow(20), las=1)
par(mfrow = c(1, 1))
####============================================================
```
\normalsize

\subsection{Mosaic grid plots for the structure of OpRisk portfolio by traded \texttt{TradeStatus}, \texttt{TraderId} by the number of realised losses vs pending loss/near misses}
\label{ssec:Mosaic cross-sectional plot}

Figures \ref{Mosaic_Instr_Trd_Tec} on page \pageref{Mosaic_Instr_Trd_Tec}:

\small
```{r, eval=FALSE, echo=TRUE}
# Contingency Table
library(vcd)
STD <- structable(~TradeStatus + TraderId + LossIndicator, data = projdata)
par(cex.axis = 1.5, cex.lab = 0.1)
# Mosaic plot
MS01 <- mosaic(STD, condvars = 'TradeStatus', col=rainbow(20), 
      split_horizontal = c(TRUE, FALSE, TRUE), shade = TRUE, legend = TRUE)
MS01
```
\normalsize

